What is MaxEnt?

### 2015-06-15 ms.tex
Intro words, Jaynes 2003 reference

@@

\bibitem[Jaynes(1979)]{stand_on_entropy} Jaynes, E. T., 1979, ``Where do we Stand on Maximum Entropy?'' in The Maximum Entropy Formalism, R. D. Levine and M. Tribus (eds.), M. I. T. Press, Cambridge, MA, p. 15
\end{thebibliography}

>>>>

The principle of maximum entropy (MaxEnt) is an idea in probability theory
that is usually associated with \citet{jaynes}. The principle may be used
to {\it assign} or {\it update} a
subjective\footnote{in the sense that the probability distribution is a model
of the state of uncertainty of an idealised rational agent.}
probability distribution when you obtain a certain kind of information
called {\it testable information}.

@@

\bibitem[Jaynes(1979)]{stand_on_entropy} Jaynes, E. T., 1979, ``Where do we Stand on Maximum Entropy?'' in The Maximum Entropy Formalism, R. D. Levine and M. Tribus (eds.), M. I. T. Press, Cambridge, MA, p. 15

\bibitem[Jaynes(2003)]{jaynes} Jaynes, E. T., 2003, ``Probability Theory:
The Logic of Science'', ed. G.~Larry~Bretthorst, Cambridge University Press

\end{thebibliography}
